Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-03 SWoPP2018 Paper/paper.tex
added framework overview

\subsection{FPGA NN Framework}
The goal of this framework is generality, in so far that when finished one can select which numerical format one wants to use and then compile the OpenCL kernel for that format. %TODO OpenCL explanation
While keeping the same API, so easier comparative research can be done on training performance using the different formats. % TODO Figure (Arthur?)

>>>>

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{training_overview.pdf}
  \caption{Overview over our framework, showing blocks existing (white) and components currently worked on (gray)}\label{fig:overview}
\end{figure*}

\subsection{FPGA Neural Network Framework}
We aspire to create a neural network framework that allows design-space exploration with different numerical data formats. Our framework, illustrated in Figure~\ref{fig:overview}, consists of a number of components. We have chosen to rely on Python as the high-level frontend for our frameowork. It is through python that a user create a networks, selects inputs, and decides what data formats to use. Once a particular configuration is selected, our framework generates data-type oblivious training and inference code that targets Intel's OpenCL SDK for FPGAs. By data-type oblivious we mean that all operations associated with any particular data-type representation remain unresolved at the point of creation, as they will not depend on any of the native data-types or functionality of the OpenCL language. Instead, our Python framework invokes a Data-type selector, which automatically generates a low-level hardware description lanague (HDL) library that contain commonly used operators for the selected data-type. Once the Register-Transfer Level (RTL) library has been generated, it is merged with the data-type oblivious OpenCL template to yield the final description, which now can be synthesized using EDA tools and used. Invisible to the user, our host runtime system handles all communication, invocation and control over the FPGA from the host side.

The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.
